The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-17 exp-resurgence.tex
State the Borel regularity result we just proved

%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
\end{proof}
\begin{theorem}[restatement of \ref{thm:has_ae_ODE}]
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

@@

Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\llbracket \zeta, \zeta^{-1} \rrbracket$. The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\llbracket \zeta \rrbracket$. Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. \textcolor{orange}{[How to rephrase without formal Laplace transform? Conclusion is stronger than statement; change statement accordingly.]}

>>>>

%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
\end{proof}
We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, and the Borel sum of $\series{\Psi}_\alpha$ is $\Psi_\alpha$.
\end{theorem}
\begin{proof}
Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}. By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$. Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4. To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.

@@

Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\llbracket \zeta, \zeta^{-1} \rrbracket$. The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\llbracket \zeta \rrbracket$. Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$. \textcolor{orange}{[How to rephrase without formal Laplace transform?]}

Now, let's take the Borel sum of $\series{\Psi}_\alpha$. The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$. By definition, the sum of $\series{\psi}_\alpha$ is $\psi_\alpha$, and the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$ is $\Psi_\alpha$.
